Naming Anonymous JavaScript Functions

### 2011-04-11 papers/splash-wavefront2011/sigplanconf-template.tex
evaluation table is updated.

Next we rank the collected identifiers and strings to elide less relevant data from the summary. Finally we concatenate the items with marker symbols to construct a string from the consumption summary. The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens. It compactly explains the function object creation, consumption and assignment.

@@

\begin{table}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & NoName & Freq=1 & Freq\textless=2 & Avg/lng Len  \\ 
  \hline 
   Closure & 10 & 8874(99\%) & 8960(99.7\%) & 35/101 \\ 
  \hline 
   DoJo & 390 & 13189(83\%) & 13761(87\%) & 36/162 \\ 
  \hline 
   ExtJS & 231 & 33960(93\%) & 35240(96\%)  & 25/91\\ 
  \hline 
   Firebug & 10 & 2976(99\%) & 3002(99.5\%) & 36/140 \\ 
  \hline 
   jQuery & 8  & 335(84\%) & 381(95\%) & 18/65 \\ 
  \hline 
   MochiKit &  16 & 1622(89\%) & 1714(84\%) & 22/80 \\ 
  \hline 
   MooTools & 18  & 462(75\%) & 546(88\%) & 14/73 \\ 
  \hline 
   Prototype & 19  & 353(80\%) & 383(87\%) & 25/88 \\ 
  \hline 
   Scriptaculous &  19 & 779(88\%) & 819(93\%) & 27/132 \\ 
  \hline 
   YUI & 15 & 19204(90\%) & 20298(95\%)  & 37/145 \\ 
  \hline 
   All & 736(1\%) & 81754(91\%) & 85104(95\%) &  \\ 
  \hline 
  \end{tabular}
  }
 \label{firebug} 
\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longes length of produced names for each project.}
\end{table}    
\subsection{Produced Names Characteristics}

@@

\begin{table}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l |}
  \hline
   Project & Equal & Similar & Fbug NoName  \\ 
  \hline 
   Closure & 5 & 8528(95\%) & 312(3\%) \\ 
  \hline 
   DoJo & 1853(12\%) & 12182(77\%) & 3362(2\%)  \\ 
  \hline 
   ExtJS & 3376(9\%) & 17579(48\%) & 1543(4\%)  \\ 
  \hline 
   Firebug & 271(9\%) & 2839(94\%) & 167(5\%)  \\ 
  \hline 
   jQuery & 119(30\%) & 282(70\%) & 95(24\%) \\ 
  \hline 
   MochiKit & 609(33\%) &  1568(86\%) & 202(11\%) \\ 
  \hline 
   MooTools & 250(40\%) & 446(72\%) & 121(19\%)  \\ 
  \hline 
   Prototype & 33(7\%) & 310(70\%) & 125(28\%)  \\ 
  \hline 
   Scriptaculous & 36(4\%) &  652(74\%) & 195(22\%)  \\ 
  \hline 
   YUI & 51 &  11808(55\%) & 3317(15\%) \\ 
  \hline 
   All & 6603(7\%) & 56194(62\%) & 9439(10\%) \\ 
  \hline 
  \end{tabular}
  }
 \label{firebug} 
\caption{Number of functions received the same or similar names to FOC approach and no name by Firebug {\small \texttt{guessFunctionName()}}.}
\end{table}

>>>>

Next we rank the collected identifiers and strings to elide less relevant data from the summary. 
\begin{verbatim}
	salmir	if during the walking up we reach a "return" node and the outer function is a "closure function" we jump to the parent node of "closure function"
	johnjbarton	inside the while correct?
	salmir	right.
	salmir	there is also another effect, but not in the algorithm. The parent context name will become the closure functions parent context name.
johnjbarton	can we handle this case with the end of the while loop:
	johnjbarton	n = n.parent
	salmir	yes.
	johnjbarton	to
	johnjbarton	n = getNextNode(n)
	salmir	getParentNode();
	johnjbarton	then explain getNextNode is either n.parent or the funky other thing

		so now we are done with the summary and we process it with another algorithm
	salmir	yes.drop case 2 unless we have at least one of 1 or 3?
	salmir	yes.
	johnjbarton	why?because the name from the function call is less valuable than the target
	salmir	because those identifiers give some information about the function object directly, but the function calls are indirect.
johnjbarton	ok we need an example for both paths
salmir	line 13
	salmir	we drop op()
	salmir	for the other case when we keep function call, you can use figure 4.
	salmir	jquery example.
	johnjbarton	which one, inner or outer
	salmir	inner
	johnjbarton	I don't see it
	salmir	right, outer.

salmir	if there are more than on function call we just use the closes one to the function defintion.
	salmir	foo(bar(baz("MyFun", function(){})) -> baz[MyFun]()
	johnjbarton	so if we have two case 2 and zero 1 or 3, then pick the early case 2?
	salmir	yes.

johnjbarton	so the next step is to concatenate
	johnjbarton	and you just remove dups or?
	salmir	just that.
	johnjbarton	and the reason for << is no identifier is found
	salmir	yes, or internal nodes.
	johnjbarton	what is an internal node?>
	salmir	foo(bar(baz((function(){})))
	salmir	<<<
	salmir	myObject = foo(bar(baz((function(){})))
        salmir	here foo, bar baz all are internal nodes.
	salmir	so we just get myObject< as name
\end{verbatim}
Finally we concatenate the items with marker symbols to construct a string from the consumption summary. The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens. It compactly explains the function object creation, consumption and assignment.

@@

\begin{table*}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
  \hline
   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name       &    ~ FBUG Name        & Duplicates  & Avg/lng       & Avg/lng  \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8528(95\%)         & 113(1\%)    & 33/76         & 35/101 \\ 
  \hline 
   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    12182(77\%)        & 2677(17\%)  & 35/81         & 36/162 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    17579(48\%)        & 2573(7\%)   & 22/65         & 25/91  \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2839(94\%)         & 2976(1\%)   & 27/70         & 36/140 \\ 
  \hline 
   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    282(70\%)          & 64(16\%)    & 14/50         & 18/65  \\ 
  \hline 
   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    1568(86\%)         & 207(11\%)   & 17/49         & 22/80   \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    446(72\%)          & 156(25\%)   & 12/36         & 14/73   \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(0.8\%)         &    310(70\%)          & 89(20\%)    & 23/55         & 25/88    \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(0.8\%)         &    652(74\%)          & 105(12\%)   & 22/55         & 27/132   \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    11808(55\%)        & 2220(10\%)  & 16/114         & 37/145  \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    56194(62\%)        & 8264(9\%)   &                &          \\ 
  \hline       
  \end{tabular}
  }
 \label{firebug} 
\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longest length of produced names for each project.}
\end{table*}    
\subsection{Produced Names Characteristics}

@@
